The Globular Cluster System of the Auriga Simulations

### 2019-01-05 Partial/FeH_logM.tex
Ran 2D FeH Rgc analysis

\afterpage{%
\section{Distribution of metallicity [Fe/H]}
\label{sec:FeH}
\thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-all}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit0}.png}
    \caption{
        \scriptsize \emph{Left:} Mass-weighted [Fe/H]-R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} There seems to be a trent of constant mass increase with
        increasing metallicity in the range -3 to -1, and roughly 1 order of 
        magnitude scatter in mass normalization. We use linear regression to 
        obtain log$_{10}$(mass normalization) (i.e. we fit $a\cdot(x+3) + b$)
        \label{fig:todo1}
    }

    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit1}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
    \caption{
        \scriptsize \emph{Left:} Scatter plot of log$_{10}$(mass normalization)
        [i.e. $b$ obtained above] against the virial mass M$_{200,c}$ of the 
        Auriga haloes. We use linear regression to see whether there is a 
        correlation, and find $a_2 = 0.00388$, $b_2 = 6.597$. Colours indicate 
        resolution: L3 red, L4 green, and L5 blue.
        \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
        `central' x value; yellow region 1$\sigma$ interval; blue dashed lines 
        intrinsic scatter. Fake Error bars (1\% of the obtained values).
        \label{fig:todo2}
    }

@@

\afterpage{%
\section{Distribution of Galactocentric radii R$_{\rm GC}$}
\label{sec:Rgc}
\thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-errorbar-trim}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} 
        \label{fig:todo7}
    }

@@

\section{Distribution of [Fe/H]-R$_{\rm GC}$}
\label{sec:FeH-Rgc}

>>>>

\afterpage{%
\section{Distribution of metallicity [Fe/H]}
\label{sec:FeH}
\thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_plot-all}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit0}.png}
    \caption{
        \scriptsize \emph{Left:} Mass-weighted [Fe/H] distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} There seems to be a trent of constant mass increase with
        increasing metallicity in the range -3 to -1, and roughly 1 order of 
        magnitude scatter in mass normalization. We use linear regression to 
        obtain log$_{10}$(mass normalization) (i.e. we fit $a\cdot(x+3) + b$)
        \label{fig:todo1}
    }

    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit1}.png}
    \includegraphics[width=0.49\textwidth]{{logMFeH_OldStars_normalization_fit3}.png}
    \caption{
        \scriptsize \emph{Left:} Scatter plot of log$_{10}$(mass normalization)
        [i.e. $b$ obtained above] against the virial mass M$_{200,c}$ of the 
        Auriga haloes. We use linear regression to see whether there is a 
        correlation, and find $a_2 = 0.00388$, $b_2 = 6.597$. Colours indicate 
        resolution: L3 green, L4 orange, and L5 blue.
        \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
        `central' x value; yellow region 1$\sigma$ interval; blue dashed lines 
        intrinsic scatter. Fake Error bars (1\% of the obtained values).
        \label{fig:todo2}
    }

@@

\afterpage{%
\section{Distribution of Galactocentric radii R$_{\rm GC}$}
\label{sec:FeH}
% \thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit0-trim}.png}
    \caption{
        \scriptsize \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} We use linear regression to obtain log$_{10}$(mass
        normalization) in the domain 0-100 kpc (i.e. we fit $ax+b$ with $a=0$)
        \label{fig:todo1}
    }

    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit1}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_normalization_fit3}.png}
    \caption{
        \scriptsize \emph{Left:} Scatter plot of log$_{10}$(mass normalization)
        [i.e. $b$ obtained above] against the virial mass M$_{200,c}$ of the 
        Auriga haloes. We use linear regression to see whether there is a 
        correlation, and find $a_2 = 0.005$, $b_2 = 8.716$. Colours indicate 
        resolution: L3 green, L4 orange, and L5 blue.
        \emph{Right:} Same `data', but MCMC fit. Red dotted line shows 
        `central' x value; yellow region 1$\sigma$ interval; blue dashed lines 
        intrinsic scatter. Fake Error bars (1\% of the obtained values).
        \label{fig:todo2}
    }

    { \centering
    \includegraphics[width=0.4\textwidth]{{logMRgc_OldStars_normalization_fit2}.png}
    \caption{
        \scriptsize TODO: corner plot of the MCMC. Conclusion: there is a positive 
        correlation of the normalization of old stellar mass with the virial
        mass $M_{200,c}.$
        \label{fig:todo3}
    }
    }
\end{figure*}
\clearpage
}
\clearpage

\afterpage{%
\label{sec:Rgc}
% \thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-errorbar-trim}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} 
        \label{fig:todo7}
    }

@@

\afterpage{%
\section{Distribution of [Fe/H]-R$_{\rm GC}$}
\label{sec:FeH-Rgc}

% \thispagestyle{empty}
\begin{figure*}[h!]
    { \centering
    \includegraphics[width=0.49\textwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        Repetition of Fig.~\ref{fig:MW-M31-Rgc-FeHRgc} (right) for (convenient)
        comparison. Note that the limits on the color bar are different for the 
        observations and the mean of all simulations below.
        \label{fig:todo1}
    }
    }

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{mean value} 
        (of 40 Auriga haloes)
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_mean}.png}
    \caption{
        \emph{Left:} Same figure, but for old insitu stars.
        \emph{Right:} Same figure, but for old accreted stars.
        \label{fig:todo2}
    }

\end{figure*}
\clearpage
}
\clearpage

\afterpage{%
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_istars_std}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_std}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$-[Fe/H] distribution of 
        all Auriga haloes (level 3, 4 and 5). Here we consider all stars
        in all simulations and color-code the \textbf{standard deviation} 
        (of 40 Auriga haloes)
        \emph{Right:} Same figure, but for old ($>$~10~Gyr) stars.
        \label{fig:todo2}
    }

    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_insitu-old_std}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_accreted-old_std}.png}
    \caption{
        \emph{Left:} Same figure, but for old insitu stars.
        \emph{Right:} Same figure, but for old accreted stars.
        \label{fig:todo2}
    }

    \includegraphics[width=0.32\textwidth]
        {{Au3-23_RgcFeH_HistogramMassWeighted_iold_16bins_comparison}.png}
    \includegraphics[width=0.32\textwidth]
        {{Au3-23_RgcFeH_HistogramMassWeighted_insitu-old_16bins_comparison}.png}
    \includegraphics[width=0.32\textwidth]
        {{Au3-23_RgcFeH_HistogramMassWeighted_accreted-old_16bins_comparison}.png}
    \caption{
        Lazy comparison to check whether there is more (total) mass in the simulated
        star particles than in the MW GCS. Green means yes; red means no. We
        check this for all fourty haloes individually to answer the question
        whether the star formation model implemented in the Auriga simulations
        can produce 'stars in the right place'.
        \emph{Left:} Au3-23, old stars.
        \emph{Mid:} Au3-23: old insitu stars.
        \emph{Right:} Au3-23: old accreted stars.
        \label{fig:todo2}
    }

\end{figure*}
\clearpage
}
\clearpage

\appendix
\section{MCMC}
Bayesian  code  as  described  in  and  distributed  by \citet{2012A&A...547A.117A}
and used in \citet{2014A&A...568A..23A} for analysing the determination 
of the evolution of the richness-mass scaling. Code used is \textsc{jags} 
\citep{plummer2003jags}, and the Python wrapper \textsc{pyjags}, and
for laziness \textsc{corner} \citep{corner} for visual inspection.

Text could be something like the following.
Blabla ``we adopt this Bayesian approach.'', and blabla
``We assume weak priors on slope, intercept, and intrinsic scatter and solve for 
all variables at once. We used a computationally inexpensive 10 thousand long 
Markov chain Monte Carlo, discarding the initial 3 thousand elements used for 
burn-in. By running multiple chains, we checked that convergence is already 
achieved with short chains.''
